Selecting and Controlling Physical Devices Through a Head-Mounted Display with Infrared Targeting

### 2013-09-02 doc/sigchi14/relatedwork.tex
bjoern's pass at overall narrative
small tweaks

@@

\subsection{Augmented Reality Interfaces}
\bjoern{most of the prior headmounted work is in the AR space. I don't know much about it yet.}

>>>>

Commercial universal control applications for smart phones are also available (e.g., Belkin WeMo\footnote{http://www.belkin.com/us/wemo}), though they usually do not offer spatial selection of target devices, forcing users to browse through lists of configured devices instead.

@@

\subsection{Augmented Reality Interfaces}
\bjoern{most of the prior head-mounted work is in the AR space. I don't know much about it yet, but Kortuem~\cite{kortuem_context-aware_1998} might be a good starting point.}
